True versus apparent shapes of bow shocks

### 2018-02-26 papers/Papers1234/sec-conclusions.tex
Make new section for 000-400 comparison
Remove RA, Dec axes and add scale bar and compass

>>>>

\section{Example application to observations}
\label{sec:obs}

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/new-000-400-multi-fig}
  \caption{Example empirical determination of planitude and alatude
    for an observed bow shock.  An \textit{HST} H\(\alpha\) image (ACS
    F658N filter) of M42~000-400 is shown in color scale and contours
    \citep{Bally:2006a}.}
  \label{fig:000-400-fit}
\end{figure*}

As an example of measuring the projected planitude and alatude of a
real bow shock, we present an analysis of the H\(\alpha\) emission arc
associated with the proplyd M42~000-400 in the west of the Orion
Nebula \citep{Bally:2000a},\footnote{%
  The same object is listed as 4596-400 in some catalogs, such as
  \citet{Ricci:2008a}.  } %
which was used as an archetype of the bow shape in
Figure~\ref{fig:bow-terminology}.
